---
title: "CCP DEEP - redoing with 5000 iterations; getting rhat and other diagnostics"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
    toc_float: yes
---

This code was executed on the results after running DEEPEst with 5000 iterations on CCP0, CCP1, CCP3, and CCP4 (the 4 studies in the current version of the paper for which DEEP estimates are important; Studies 1-4). 

Load data and packages

```{r}
library(ggplot2)
library(bayesplot)
library(DEEPEst)
library(rstan)

load("/Users/Kelle/Documents/DEEP Kellen/redo5000/Stan_Time_ccp1_EstHier8questions.Rdata")

c1est<-read.csv("/Users/Kelle/Documents/DEEP Kellen/redo5000/StanEstimates_Time_Parameters_ccp1_EstHier8questions.csv")
```


# 1. CCP1 (first study we ran and first in the paper)

## 1.1 Distribution of beta and delta
```{r}

ggplot(c1est, aes(x = beta)) + geom_density()

ggplot(c1est, aes(x = delta)) + geom_density()

```

## 1.2 Average rhat across the sample


Rstan documentation says they recommend "only using the sample if R-hat is less than 1.05". Assuming they mean average R-hat less than 1.05, we seem to pass this rule in CCP1 (barely). Antonia said rhat should be under 1, which we don't quite pass.


```{r}
#for beta
rhat(hier_time, pars = "mubeta")

#for delta
rhat(hier_time, pars = "mudelta_phi")

#for theta (the error?)
rhat(hier_time, pars = "mutheta")

```

## 1.3 Correlation between beta and delta

```{r}
#beta and delta (annual discount factor) correlation
cor(c1est$beta,c1est$delta)

#beta and daily discount rate correlation
cor(c1est$beta,c1est$r)


plot(c1est$beta,c1est$delta)


```

##  1.4 Pairs plots

Antonia does this one participant at a time, so it's not clear to me what the overall takeaway is. Seems like most pairs plots between beta and delta look okay, though beta and r looks less good (perhaps because r has big positive skew?)

First 12 participants shown below
```{r}

pairs(hier_time,pars=c("beta[1]", "r[1]", "delta[1]"))

pairs(hier_time,pars=c("beta[2]", "r[2]", "delta[2]"))

pairs(hier_time,pars=c("beta[3]", "r[3]", "delta[3]"))

pairs(hier_time,pars=c("beta[4]", "r[4]", "delta[4]"))

pairs(hier_time,pars=c("beta[5]", "r[5]", "delta[5]"))

pairs(hier_time,pars=c("beta[6]", "r[6]", "delta[6]"))

pairs(hier_time,pars=c("beta[7]", "r[7]", "delta[7]"))

pairs(hier_time,pars=c("beta[8]", "r[8]", "delta[8]"))

pairs(hier_time,pars=c("beta[9]", "r[9]", "delta[9]"))

pairs(hier_time,pars=c("beta[10]", "r[10]", "delta[10]"))

pairs(hier_time,pars=c("beta[11]", "r[11]", "delta[11]"))

pairs(hier_time,pars=c("beta[12]", "r[12]", "delta[12]"))
```



# 2. CCP3 (eye-tracking and prolific, combined)


## 2.1 Distribution of beta and delta
```{r}
load("/Users/Kelle/Documents/DEEP Kellen/redo5000/Stan_Time_ccp3_EstHier8questions.Rdata")

c3est<-read.csv("/Users/Kelle/Documents/DEEP Kellen/redo5000/StanEstimates_Time_Parameters_ccp3_EstHier8questions.csv")

ggplot(c3est, aes(x = beta)) + geom_density()

ggplot(c3est, aes(x = delta)) + geom_density()

```

## 2.2 Average rhat across the sample


Rstan documentation says they recommend "only using the sample if R-hat is less than 1.05". Assuming they mean average R-hat less than 1.05, we seem to pass this rule in CCP3.


```{r}
#for beta
rhat(hier_time, pars = "mubeta")

#for delta
rhat(hier_time, pars = "mudelta_phi")

#for theta (the error?)
rhat(hier_time, pars = "mutheta")

```

## 2.3 Correlation between beta and delta

```{r}
#beta and delta (annual discount factor) correlation
cor(c3est$beta,c3est$delta)


#beta and daily discount rate correlation
cor(c3est$beta,c3est$r)

plot(c3est$beta,c3est$delta)

```

##  2.4 Pairs plots

First 12 participants shown below

```{r}

pairs(hier_time,pars=c("beta[1]", "r[1]", "delta[1]"))

pairs(hier_time,pars=c("beta[2]", "r[2]", "delta[2]"))

pairs(hier_time,pars=c("beta[3]", "r[3]", "delta[3]"))

pairs(hier_time,pars=c("beta[4]", "r[4]", "delta[4]"))

pairs(hier_time,pars=c("beta[5]", "r[5]", "delta[5]"))

pairs(hier_time,pars=c("beta[6]", "r[6]", "delta[6]"))

pairs(hier_time,pars=c("beta[7]", "r[7]", "delta[7]"))

pairs(hier_time,pars=c("beta[8]", "r[8]", "delta[8]"))

pairs(hier_time,pars=c("beta[9]", "r[9]", "delta[9]"))

pairs(hier_time,pars=c("beta[10]", "r[10]", "delta[10]"))

pairs(hier_time,pars=c("beta[11]", "r[11]", "delta[11]"))

pairs(hier_time,pars=c("beta[12]", "r[12]", "delta[12]"))

```





# 3. CCP4 (mostly a replication of CCP1)


## 3.1 Distribution of beta and delta
```{r}
load("/Users/Kelle/Documents/DEEP Kellen/redo5000/Stan_Time_ccp4_EstHier12questions.Rdata")

c4est<-read.csv("/Users/Kelle/Documents/DEEP Kellen/redo5000/StanEstimates_Time_Parameters_ccp4_EstHier12questions.csv")

ggplot(c4est, aes(x = beta)) + geom_density()

ggplot(c4est, aes(x = delta)) + geom_density()

```

## 3.2 Average rhat across the sample

Rstan documentation says they recommend "only using the sample if R-hat is less than 1.05". Assuming they mean average R-hat less than 1.05, we seem to pass this rule in CCP4.


```{r}
#for beta
rhat(hier_time, pars = "mubeta")

#for delta
rhat(hier_time, pars = "mudelta_phi")

#for theta (the error?)
rhat(hier_time, pars = "mutheta")

```

## 3.3 Correlation between beta and delta

```{r}
#beta and delta (annual discount factor) correlation
cor(c4est$beta,c4est$delta)


#beta and daily discount rate correlation
cor(c4est$beta,c4est$r)


plot(c4est$beta,c4est$delta)

```

##  3.4 Pairs plots

First 12 participants shown below

```{r}

pairs(hier_time,pars=c("beta[1]", "r[1]", "delta[1]"))

pairs(hier_time,pars=c("beta[2]", "r[2]", "delta[2]"))

pairs(hier_time,pars=c("beta[3]", "r[3]", "delta[3]"))

pairs(hier_time,pars=c("beta[4]", "r[4]", "delta[4]"))

pairs(hier_time,pars=c("beta[5]", "r[5]", "delta[5]"))

pairs(hier_time,pars=c("beta[6]", "r[6]", "delta[6]"))

pairs(hier_time,pars=c("beta[7]", "r[7]", "delta[7]"))

pairs(hier_time,pars=c("beta[8]", "r[8]", "delta[8]"))

pairs(hier_time,pars=c("beta[9]", "r[9]", "delta[9]"))

pairs(hier_time,pars=c("beta[10]", "r[10]", "delta[10]"))

pairs(hier_time,pars=c("beta[11]", "r[11]", "delta[11]"))

pairs(hier_time,pars=c("beta[12]", "r[12]", "delta[12]"))

```




# 4. CCP0 (used New DEEP unlike 1, 3, and 4; using cash back rewards, more ecologically valid)



## 4.1 Distribution of beta and delta
```{r}
load("/Users/Kelle/Documents/DEEP Kellen/redo5000/Stan_Time_ccp0_EstHier16questions.Rdata")

c0est<-read.csv("/Users/Kelle/Documents/DEEP Kellen/redo5000/StanEstimates_Time_Parameters_ccp0_EstHier16questions.csv")

ggplot(c0est, aes(x = beta)) + geom_density()

ggplot(c0est, aes(x = delta)) + geom_density()

```

## 4.2 Average rhat across the sample


Rstan documentation says they recommend "only using the sample if R-hat is less than 1.05". Assuming they mean average R-hat less than 1.05, we pass this for delta and are almost exactly at 1.05 for beta in CCP0.


```{r}
#for beta
rhat(hier_time, pars = "mubeta")

#for delta
rhat(hier_time, pars = "mudelta_phi")

#for theta (the error?)
rhat(hier_time, pars = "mutheta")

```

## 4.3 Correlation between beta and delta

```{r}
#beta and delta (annual discount factor) correlation
cor(c0est$beta,c0est$delta)


#beta and daily discount rate correlation
cor(c0est$beta,c0est$r)

plot(c0est$beta,c0est$delta)

```

##  4.4 Pairs plots

First 12 participants shown below

```{r}

pairs(hier_time,pars=c("beta[1]", "r[1]", "delta[1]"))

pairs(hier_time,pars=c("beta[2]", "r[2]", "delta[2]"))

pairs(hier_time,pars=c("beta[3]", "r[3]", "delta[3]"))

pairs(hier_time,pars=c("beta[4]", "r[4]", "delta[4]"))

pairs(hier_time,pars=c("beta[5]", "r[5]", "delta[5]"))

pairs(hier_time,pars=c("beta[6]", "r[6]", "delta[6]"))

pairs(hier_time,pars=c("beta[7]", "r[7]", "delta[7]"))

pairs(hier_time,pars=c("beta[8]", "r[8]", "delta[8]"))

pairs(hier_time,pars=c("beta[9]", "r[9]", "delta[9]"))

pairs(hier_time,pars=c("beta[10]", "r[10]", "delta[10]"))

pairs(hier_time,pars=c("beta[11]", "r[11]", "delta[11]"))

pairs(hier_time,pars=c("beta[12]", "r[12]", "delta[12]"))

```

