---
title: "CCP 0 analysis"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '4'
    toc_float: yes
  html_notebook:
    toc: yes
    toc_depth: '4'
    toc_float: yes
---
## 1. Summary

Present bias predicts lower accuracy. The effect on a continuous measure of accuracy is robust, but on the yes/no accuracy is not particularly robust. (I pre-registered both measures.)
  
Present bias predicts less time spent searching/making credit card decision, although this is only true when we control for total time spent on the survey which was a suppressor.


  
  
Notes. The continuous accuracy measure is total costs of the credit card, so higher scores mean choosing cards with higher costs (worse choices). The categorical accuracy is yes/no where yes=1, so higher scores mean more accurate. Beta is coded with Qi's method, 1 means no present biased, 0 is the most present biased. 


```{r message=FALSE, warning=FALSE, include=FALSE}
######Script for 16 rows per person for possibly more powerful analyses (t)
library(dplyr)
library(effects)
library(lme4)
library(lmerTest)
library(e1071)
library(mediation)
library(ggplot2)
library(RCurl)

# Load data from github
ccp0<-read.csv("/Users/Kelle/Documents/ccp0_clean.csv")

#Time spent on rest of survey
ccp0$restofsurvey<-ccp0$surveytime-(ccp0$cctime/60)

ccp0$logrestofsurvey<-log10(ccp0$restofsurvey+1.85)

ccp0$cctime<-ccp0$Q181_3

ccp0$logtime<-log10(ccp0$cctime)

```

## 2. DEEP histograms

### Beta and Delta (Qi's method)
```{r}
ggplot(ccp0, aes(x = beta)) + geom_density()
ggplot(ccp0, aes(x = delta)) + geom_density()
cor.test(ccp0$beta,ccp0$delta)
```

## 3. Boxes opened and timing summary statistics 

### 3.1. Descriptive Plots and Stats for Accuracy and Time Variables

Time spent on whole survey is in minutes.
  
Time spent on credit card choice is in seconds.
  
```{r}

#Time spent on whole survey
ggplot(ccp0, aes(x = surveytime)) + geom_density()

#Time spent searching/choosing credit card
ggplot(ccp0, aes(x = cctime)) + geom_density()


#CC choice Accuracy: Continuous
hist(ccp0$ccCost,main="Credit card total costs (continuous)",xlab="Dollars",breaks=40)

#Number of participants choosing card with each level of total costs.
table(ccp0$ccCost)

#CC Choice Accuracy: Binary (yes=1/no=0)
table(ccp0$correct)


```


### 3.2 Skewness of variables

The time variables had large positive skews and log transformations work well (also pre-registered that we would log-transform if skewness was this high).

```{r echo=TRUE, message=FALSE, warning=FALSE}
skewness(ccp0$cctime)
skewness(ccp0$logtime)
skewness(ccp0$restofsurvey)
skewness(ccp0$logrestofsurvey)

```

## 4. Main Analyses 

### 4.1. Present bias predicts choosing cards with higher total costs (continuous measure of inaccuracy, which we pre-registered)

Strongest effect is on this measure   
```{r}
m1a<-lm(ccCost~beta+delta,data=ccp0)
summary(m1a)
```

### 4.2. Present bias predicts lower accuracy (binary measure of accuracy, yes/no, which we also pre-registered)


```{r}
m1b<-glm(correct~beta+delta,data=ccp0,family=binomial)
summary(m1b)
```


### 4.3. Present bias and time spent searching/choosing credit card

Effect of beta on time spent choosing is non-significant (1st model below), except when you control for total time spent on survey (2nd model below).

```{r}
m2<-lm(logtime~beta+delta,data=ccp0)
summary(m2)

#We do get an effect of present bias on less time spent making credit card choices when we control for total time spent on survey (because present-biased people spend more time on the survey overall, which suppressed the effect on credit card search time)

m2a<-lm(logtime~beta+delta+logrestofsurvey,data=ccp0)
summary(m2a)

```


###  4.4.  We get a significant indirect effect (though only when we control for time spent on rest of survey). 

(This is controlling for total time spent on survey. If we don't control for total time spent on survey, there is nothing close to an indirect effect.) 

Mediation model (ACME is the indirect effect). This was pre-registered as a "secondary analysis".

```{r}

a <- lm(logtime ~ beta+delta+logrestofsurvey, data=ccp0)
b <- lm(ccCost ~ beta+delta + logtime+logrestofsurvey, data=ccp0)

# Estimation via quasi-Bayesian approximation
contcont <- mediate(a, b, sims=5000, treat="beta", mediator="logtime")
summary(contcont)

```


## 5. Pre-registered robustness tests

### 5.1  Control for self-reported credit score (nothing changes)

```{r}

m1ac<-lm(ccCost~beta+delta+Cscore,data=ccp0)
summary(m1ac)

m1bc<-glm(correct~beta+delta+Cscore,data=ccp0,family=binomial)
summary(m1bc)

m2c<-lm(logtime~beta+delta+Cscore+logrestofsurvey,data=ccp0)
summary(m2c)

```



### 5.2  Exclude people who don't own a credit card.

Effects get slightly stronger. Yes/no accuracy goes from p=.052 to p=.02
```{r}
own<-ccp0[(ccp0$Q131==1),]


m1ae<-lm(ccCost~beta+delta,data=own)
summary(m1ae)

m1be<-glm(correct~beta+delta,data=own,family=binomial)
summary(m1be)

m2e<-lm(logtime~beta+delta+logrestofsurvey,data=own)
summary(m2e)

```


### 5.3  Exclude search time outliers.

Accuracy effects are unchanged. Search time effect goes away when we exclude the outliers who spent more than 5 min on credit card choice (goes away even when controlling for total survey time).

```{r}
exc<-ccp0[(ccp0$cctime<300),]

m1ad<-lm(ccCost~beta+delta,data=exc)
summary(m1ad)

m1bd<-glm(correct~beta+delta,data=exc,family=binomial)
summary(m1bd)

m2d<-lm(cctime~beta+delta+logrestofsurvey,data=exc)
summary(m2d)


```


###  5.4   Controlling for all of the key covariates we measured (credit score, financial literacy, numeracy, total time spent on rest of survey, income)

Only the effect on continuous credit card costs remains.

For the yes/no accuracy DV, it seems to be financial literacy and numeracy that caused the effect to go away; if you remove both those covariates, the effect reappears. If you add just one of those back in (either one), the effect goes away.

```{r}

m1af<-lm(ccCost~beta+delta+Cscore+FL_tot+Numeracy+logrestofsurvey+hh_income,data=ccp0)
summary(m1af)

m1bf<-glm(correct~beta+delta+Cscore+FL_tot+Numeracy+logrestofsurvey+hh_income,data=ccp0,family=binomial)
summary(m1bf)

m2cf<-lm(logtime~beta+delta+Cscore+FL_tot+Numeracy+logrestofsurvey+hh_income,data=ccp0)
summary(m2cf)

#financial literacy, self-reported credit scores, income category, numeracy, and time spent on the rest of the survey (not including credit card choice task)
```



## 6. Other tests (not pre-registered)

Excluding people who calculated costs with Excel or Calculator

Effects get weaker. Only the continuous costs measure remains significant.

```{r}
nocalc<-ccp0[(ccp0$calculator==0),]
nodevice<-nocalc[(nocalc$otherdev==0),]
noexcel<-nodevice[(nodevice$spreadsheet==0),]

m1ad<-lm(ccCost~beta+delta,data=noexcel)
summary(m1ad)

m1bd<-glm(correct~beta+delta,data=noexcel,family=binomial)
summary(m1bd)

m2d<-lm(logtime~beta+delta+logrestofsurvey,data=noexcel)
summary(m2d)

```


