---
title: "CCP 1 analysis"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
    toc_float: yes
  html_notebook:
    toc: yes
    toc_depth: '4'
---
## 1. Summary

Present bias predicts less search and lower accuracy.  

The effect of present bias on search is especially large for the "standard APR" attribute (significant interaction), but is positive for all four attributes.  

There is also a significant delta x introductory period interaction, just as in CCP4 (the effect of delta on search is especially large for introductory period).  


```{r message=FALSE, warning=FALSE, include=FALSE}
######Script for 16 rows per person for possibly more powerful analyses
library(dplyr)
library(effects)
library(lme4)
library(lmerTest)
library(e1071)
library(ggplot2)
library(RCurl)

# Load data from github
x <- getURL("https://raw.githubusercontent.com/decision-sciences/decision-sciences.github.io/master/CCP%20data/CCP1/ChoiceCC.csv")
cc_o1<-read.csv(text = x,stringsAsFactors = FALSE)

x <- getURL("https://raw.githubusercontent.com/decision-sciences/decision-sciences.github.io/master/CCP%20data/CCP1/ChoiceCC_o2.csv")
cc_o2<-read.csv(text = x,stringsAsFactors = FALSE)

x <- getURL("https://raw.githubusercontent.com/decision-sciences/decision-sciences.github.io/master/CCP%20data/CCP1/ChoiceCC_o3.csv")
cc_o3<-read.csv(text = x,stringsAsFactors = FALSE)

x <- getURL("https://raw.githubusercontent.com/decision-sciences/decision-sciences.github.io/master/CCP%20data/CCP1/ChoiceCC_o4.csv")
cc_o4<-read.csv(text = x,stringsAsFactors = FALSE)

x <- getURL("https://raw.githubusercontent.com/decision-sciences/decision-sciences.github.io/master/CCP%20data/CCP1/trial2.csv")
t2_cc_o1<-read.csv(text = x,stringsAsFactors = FALSE)

x <- getURL("https://raw.githubusercontent.com/decision-sciences/decision-sciences.github.io/master/CCP%20data/CCP1/trial2_o2.csv")
t2_cc_o2<-read.csv(text = x,stringsAsFactors = FALSE)

x <- getURL("https://raw.githubusercontent.com/decision-sciences/decision-sciences.github.io/master/CCP%20data/CCP1/trial2_o3.csv")
t2_cc_o3<-read.csv(text = x,stringsAsFactors = FALSE)

x <- getURL("https://raw.githubusercontent.com/decision-sciences/decision-sciences.github.io/master/CCP%20data/CCP1/trial2_o4.csv")
t2_cc_o4<-read.csv(text = x,stringsAsFactors = FALSE)

####bind files into one big R csv file.
cc<-rbind(cc_o1, cc_o2, cc_o3, cc_o4, t2_cc_o1, t2_cc_o2, t2_cc_o3, t2_cc_o4)



##remove boxes of <200 ms
#converts to difference in ms
cc$MSdiff <- ave(cc$time, cc$id, FUN=function(x) c(0, diff(x)))



#so that we can get mouseovers removed as well (i.e., when mouseout--value of next row--is less than 200)
cc$nextdiff <- c(cc$MSdiff[-1], NA)


cc<-cc[!(cc$event=="mouseout"&cc$MSdiff<200),]
cc<-cc[!(cc$event=="mouseover"&cc$nextdiff<200),]



##calculate total time each person took per trial
cc$maxes<-NA
maxes <- with(cc, tapply(time, id, max))
cc$maxes <- maxes[match(cc$id,names(maxes))]


##calculate total boxes opened
cc$newtab<-NA

newtab<-data.frame(table(cc$id[cc$event=="mouseover"]))
colnames(newtab)[1]<-"id"
colnames(newtab)[2]<-"numopened"

cc$newtab <- newtab[match(cc$id,newtab$id), ]

#make timevar with row (linenumb) identifyer
cc$linenumb <- with(cc, ave(as.character(id), id, FUN = seq_along))


# search time
cc$searchtime<-cc$maxes/1000

#sqrt transformation, which reduces skew
cc$numopened<-cc$newtab[,2]
cc$sqrtnumopened<-sqrt(cc$numopened)

#sqrt transformation, which reduces skew
cc$sqrttime<-sqrt(cc$searchtime)


##add variable whether they got it correct
cc$correct<-NA
cc$correct<-0


cc$correct[cc$expname=="ChoiceCC"&cc$choice=="OptionA-Gloss"]<-1
cc$correct[cc$expname=="ChoiceCC_o2"&cc$choice=="OptionA-Anywhere"]<-1
cc$correct[cc$expname=="ChoiceCC_o3"&cc$choice=="OptionA-Ascent"]<-1
cc$correct[cc$expname=="ChoiceCC_o4"&cc$choice=="OptionA-Journey"]<-1

cc$correct[cc$expname=="ChoiceCC_trial2"&cc$choice=="OptionC-Sequin"]<-1
cc$correct[cc$expname=="ChoiceCC_trial2_o2"&cc$choice=="OptionC-Polaris"]<-1
cc$correct[cc$expname=="ChoiceCC_trial2_o3"&cc$choice=="OptionC-Midnight"]<-1
cc$correct[cc$expname=="ChoiceCC_trial2_o4"&cc$choice=="OptionC-Surge"]<-1

# More cleaning 

###Adding the time preference and Qualtrics data to the seach data

ccwide<-read.csv("/Users/kelle/Documents/credit card wave short, merged.csv")


##DOUBLE CHECK THIS; may have changed when I changed the structure of this script.
#removes the ones who did not finish the study; 

qualips<-unique(ccwide$V6)

cc2<-subset(cc, (cc$ip %in% ccwide$V6))

cc<-cc2

#4 IP addresses are in qualtrics but not CC; which ones? 207.244.77.46; 198.15.118.142; 108.170.8.155; 104.236.74.212
fourmissing<-subset(qualips, !(qualips %in% c(cc$ip)))

ccwide<-subset(ccwide, !(ccwide$V6 %in% c(fourmissing)))



ccwide$annfactorold<-ccwide$annualfactor
ccwide$delta<-ccwide$new_annualfactor

ccwi<-ccwide[,1:400]

full<-merge(cc, ccwi, by.x="ip", by.y="V6")

full$hierbeta<-full$new_beta



#remove everything except fixations in the 16 boxes
#remove the mouseover, leaving just the mouseouts
full<-full[!(full$event=="mouseover"),]
full<-full[!(full$event=="onload"),]
full<-full[!(full$event=="subject"),]
full<-full[!(full$event=="order"),]
full<-full[!(full$event=="events"),]
full<-full[!(full$event=="onclick"),]
full<-full[!(full$event=="submit"),]




##count the mouseouts in each box
full16<-full %>% group_by(id.x, name) %>% mutate(fixations = n())

unique(full16$name)

#down to just 16 per trial (32 per ID)

full16$idname<-paste0(as.character(full16$id.x)," ", as.character(full16$name))
full16$first3<-substr(full16$name,start=1,stop=3)

full16oneper<-full16[,]

full16one<-full16oneper[!(full16oneper$first3=="Opt"), ]
full16o<-full16one[!duplicated(full16one$idname), ]

f16<-full16one[!duplicated(full16one$idname), ]


#problem: the above method results in 0 fixation things getting removed; ideally we would have 16 lines per person (one for each box), including boxes that were looked at 0 times.

f16$f3<-NA
f16$f3[f16$first3=="Ann"]<-"Ann"
f16$f3[f16$first3=="iAP"]<-"iAP"
f16$f3[f16$first3=="iPe"]<-"iPe"
f16$f3[f16$first3=="1-A"|f16$first3=="2-A"|f16$first3=="3-A"|f16$first3=="4-A"]<-"APR"

f16$f3<-as.factor(f16$f3)

f16$dummyannual<-NA
f16$dummyannual<--.5
f16$dummyannual[f16$first3=="Ann"]<-.5

f16$dummyintro<-NA
f16$dummyintro<--.5
f16$dummyintro[f16$first3=="iAP"]<-.5

f16$dummyperiod<-NA
f16$dummyperiod<--.5
f16$dummyperiod[f16$first3=="iPe"]<-.5

f16$dummystd<-NA
f16$dummystd<--.5
f16$dummystd[f16$first3=="1-A"|f16$first3=="2-A"|f16$first3=="3-A"|f16$first3=="4-A"]<-.5

f16$first3[f16$first3=="1-A"|f16$first3=="2-A"|f16$first3=="3-A"|f16$first3=="4-A"]<-"APR"

```
## 2. DEEP histograms

### 2.1. Beta using Qi's method
```{r}
ggplot(f16, aes(x = hierbeta)) + geom_density()
ggplot(f16, aes(x = new_annualfactor)) + geom_density()
cor.test(f16$hierbeta,f16$new_annualfactor)
```

### 2.2. Beta and delta using Dan's method 
```{r}
ggplot(f16, aes(x = beta)) + geom_density()
ggplot(f16, aes(x = annualfactor)) + geom_density()
cor.test(f16$beta,f16$annualfactor)
```

## 3. Boxes opened and timing summary statistics 

### 3.1. Summaries of boxes opened and time searching

```{r}
#Boxes opened (raw count)
summary(cc$numopened)

#Boxes opened (transformed to reduce skewness)
summary(cc$sqrtnumopened)

#Time spent searching per trial (raw count)
summary(cc$searchtime)

#Time spent searching per trial (transformed to reduce skewness)
summary(cc$sqrttime)


```

### 3.2. Histograms 

Histograms of raw and transformed number of boxes opened (first two) and time spent searching (second two).  

```{r}
#Hist of raw boxes opened
hist(cc$numopened,main="Boxes opened", xlab = "Boxes opened (raw)",yaxt='n')

#Transformed boxes opened
hist(cc$sqrtnumopened, main="Transformed boxes opened", xlab = "Sqrt boxes opened")

#Hist raw time searching
hist(cc$searchtime, main="Search time", xlab = "Time searching (raw)",yaxt='n')

# Histogram transformed time searching
hist(cc$sqrttime, main="Transformed search time", xlab = "Sqrt time searching",yaxt='n')
```

### 3.3 Skewness of variables

```{r message=FALSE, warning=FALSE, include=FALSE}
f16$lognumopened<-log10(f16$numopened+1)

skewness(f16$sqrtnumopened)
skewness(f16$numopened)
skewness(f16$lognumopened)

f16$logtime<-log10(f16$searchtime+1)

skewness(f16$sqrttime)
skewness(f16$searchtime)
skewness(f16$logtime)

skewness(f16$fixations,na.rm=TRUE)

f16$sqrtfixations<-sqrt(f16$fixations)
skewness(f16$sqrtfixations,na.rm=TRUE)

f16$logfixations<-log10(f16$fixations+1)
skewness(f16$logfixations,na.rm=TRUE)
```

## 4. Inferential tests: Old format 


### 4.1. Present bias predicts less search 

```{r}
m1<-lmer(sqrtnumopened~hierbeta+delta+(1|ip),data=f16)
summary(m1)

m1a<-lmer(logtime~hierbeta+delta+(1|ip),data=f16)
summary(m1a)
```


### 4.2. Present bias predicts lower accuracy

Summaries of coefficients for mixed-effects models below.   
```{r}
m1b<-glmer(correct~hierbeta+delta+(1|ip),data=f16,family=binomial)
summary(m1b)
```


## 5. New inferential analyses: Search x Attribute

### 5.1. Mixed Model(s)

The first model (m6) has the attribute box type coded with contrast codes centered at 0, while the second (m7) has attribute box type coded as a factor with 4 levels.  

```{r}
f16$hierbeta.c<-f16$hierbeta-mean(f16$hierbeta,na.rm=TRUE)
f16$delta.c<-f16$delta-mean(f16$delta,na.rm=TRUE) #changed "hierdelta" to "delta" --Nate 6/19/2019
#dummys already centered so removed the "-.5" from 4 lines below -- Nate 6/19/2019 
f16$standard.c<-f16$dummystd
f16$intro.c<-f16$dummyintro
f16$period.c<-f16$dummyperiod
f16$annualfee.c<-f16$dummyannual

# Remade f16$attbox based on f16$f3 which is based on f16$first3
f16$attbox<-NA
f16$attbox[f16$f3=="APR"]<-"APR"
f16$attbox[f16$f3=="Ann"]<-"AnnualFee"
f16$attbox[f16$f3=="iAP"]<-"IntroRate"
f16$attbox[f16$f3=="iPe"]<-"IntroPeriod"

f16$attbox<-as.factor(f16$attbox)

## m6 written with attbox coded as a series of contrast codes centered at 0
m6<-glmer(fixations~hierbeta.c*standard.c+hierbeta.c*period.c+hierbeta.c*intro.c+delta.c*standard.c+delta.c*period.c+delta.c*intro.c+(1|ip),data=f16,family=poisson,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(m6)

## rewrote model 6 with attbox as a factor.  Coefficients for beta and delta are different, but all interactions are the same.  
m7 <- glmer(fixations ~ hierbeta.c*attbox + delta.c*attbox +(1|ip), data = f16, family = poisson, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(m7)



```

### 5.2. Relationship between beta and search for each attribute 

Beta predicts more search for all four attributes, but especially for APR.

```{r}
plot(Effect(c("hierbeta.c", "attbox"), m7))
```

### 5.3. Relationship between delta and search for each attribute 

Plotting that delta x introductory period interaction.

The simple effect of delta on search when attribute=introductory period actually isn't significant though. But the interaction is.

```{r}
plot(Effect(c("delta.c", "attbox"), m7))

f16$dummystd<-f16$dummystd+.5
f16$dummyannual<-f16$dummyannual+.5
f16$dummyintro<-f16$dummyintro+.5
f16$dummyperiod<-f16$dummyperiod+.5

#check whether delta significantly increases search 
#that is, the simple effect of delta when attribute type is intro period (look at "delta.c" line in the m9 output for that simple effect)
m9<-glmer(fixations~delta.c*dummystd+delta.c*dummyannual+delta.c*dummyintro+(1|ip),data=f16,family=poisson,control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(m9)

```

