---
title: "CCP 3 analysis"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 4
    toc_float: yes

---
## 1. Summary

Present bias predicts less search, but not lower accuracy.  

The effect of present bias on search is not moderated by data source (eye-tracking vs. mouselabweb) and if anything is slightly larger among the eye-tracking participants.  

There is one present bias x attribute type interactions, although different than in CCP1 (effect of present bias on search is less true for annual fee than the other attributes (in CCP1 the interaction was with intro rate not annual fee).


```{r message=FALSE, warning=FALSE, include=FALSE}
######Script for 16 rows per person for possibly more powerful analyses
library(dplyr)
library(effects)
library(lme4)
library(lmerTest)
library(e1071)
library(ggplot2)

f16<-read.csv("/Users/Kelle/Documents/ccp3all_2019-09-07.csv")

#f16<-read.csv("/Users/Kelle/Documents/ccp3all.csv")

#problem: the above method results in 0 fixation things getting removed; ideally we would have 16 lines per person (one for each box), including boxes that were looked at 0 times.

f16$f3<-NA
f16$f3[f16$fixnumb<5]<-"iAP"
f16$f3[f16$fixnumb<9&f16$fixnumb>4]<-"iPe"
f16$f3[f16$fixnumb<13&f16$fixnumb>8]<-"APR"
f16$f3[f16$fixnumb>12]<-"Ann"

f16$f3<-as.factor(f16$f3)

f16$dummyannual<-NA
f16$dummyannual<--.5
f16$dummyannual[f16$f3=="Ann"]<-.5

f16$dummyintro<-NA
f16$dummyintro<--.5
f16$dummyintro[f16$f3=="iAP"]<-.5

f16$dummyperiod<-NA
f16$dummyperiod<--.5
f16$dummyperiod[f16$f3=="iPe"]<-.5

f16$dummystd<-NA
f16$dummystd<--.5
f16$dummystd[f16$f3=="APR"]<-.5


```
## 2. DEEP histograms

### 2.1. Beta (Qi's method)
```{r warning=FALSE}
ggplot(f16, aes(x = newbeta)) + geom_density()
ggplot(f16, aes(x = delta)) + geom_density()
cor.test(f16$newbeta,f16$delta)
```


## 3. Boxes opened and timing summary statistics 

### 3.1. Summaries of boxes opened and time searching

```{r}
f16$logfixations<-log10(f16$fixations+1)

#Fixations per box (raw count)
summary(f16$fixations)

#Log fixations per box (log-transformed to reduce skewness)
summary(f16$logfixations)

```

### 3.2. Histograms 

Histograms of raw and transformed number of boxes opened (first two) and time spent searching (second two).  

```{r echo=FALSE}
#Hist of raw fixations/boxes opened per box
hist(f16$fixations,main="Fixations per box",xlab="Fixations per box",breaks=40,xlim=c(0,20))


#Fixations per trial (untransformed)
hist(f16$totalfix,main="Fixations per trial",xlab="Fixations per trial",breaks=50,xlim=c(0,120))
```

### 3.3 Skewness of variables

Suggests we should use log-transformations, since they are the least skewed. If we follow the rules from the pre-registration for determining this, use log-transformations in this study.

```{r echo=TRUE, message=FALSE}

skewness(f16$sqrtfix)
skewness(f16$totalfix)
skewness(f16$logfix)

skewness(f16$sqrttime)
skewness(f16$searchtime)
skewness(f16$logtime)

skewness(f16$fixations,na.rm=TRUE)

f16$sqrtfixations<-sqrt(f16$fixations)
skewness(f16$sqrtfixations,na.rm=TRUE)


skewness(f16$logfixations,na.rm=TRUE)

```

## 4. Old style inferential tests (1 line per trial)

### 4.1 Present bias predicts fewer total fixations/box openings and less time spent on the task

```{r}
f16$newbeta.c<-f16$newbeta-mean(f16$newbeta,na.rm=TRUE)
f16$delta.c<-f16$delta-mean(f16$delta,na.rm=TRUE) 

m1 <- lmer(logfix ~ newbeta.c*datasource+delta.c+(1|RecordingName), data = f16, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(m1)

m2 <- lmer(logtime ~ newbeta.c*datasource+(1|RecordingName), data = f16, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(m2)

#still need to run a robustness test excluding search time outliers, since there were a couple very extreme search times.
```


### 4.2. Present bias does not predict accuracy in this study.

   
```{r}
m3 <- glmer(correct ~ newbeta.c*datasource+delta.c+(1|RecordingName), data = f16, family=binomial,control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(m3)


#m1b<-glmer(correct~newbeta+delta+(1|RecordingName),data=f16,family=binomial)
#summary(m1b)
```


## 5. Key Inferential Tests (16 lines per person, includes interactions with datasource and type of attribute box)

### 5.1. Mixed Models

Present bias predicts less search, and there is no significant interaction with whether it's eye-tracking or mouse-tracking.

People clearly do examine many more boxes in eye-tracking than mouselabweb (datasource effect).

There is one interaction between beta and attribute type, however not what we find in CCP1. Luckily, these were exploratory anyway; we didn't pre-register any interactions with attribute type.

The first model (m4) is a simpler model, with just the beta and beta x datasource (eye-tracking vs. mouse-tracking) interaction

The second model (m5) includes all interactions with type of attribute box, etc. The second model didn't converge when tried as a Poisson (even with the "bobyqa" fix that has worked in the past); not too surprising it didn't converge given that there are 24 predictors when including all 4 box types and all interactions with beta, delta, and datasource.
 

```{r}
f16$newbeta.c<-f16$newbeta-mean(f16$newbeta,na.rm=TRUE)
f16$delta.c<-f16$delta-mean(f16$delta,na.rm=TRUE) 
#dummys already centered so removed the "-.5" from 4 lines below 
f16$standard.c<-f16$dummystd
f16$intro.c<-f16$dummyintro
f16$period.c<-f16$dummyperiod
f16$annualfee.c<-f16$dummyannual

# Remade f16$attbox based on f16$f3 which is based on f16$first3
f16$attbox<-NA
f16$attbox[f16$f3=="APR"]<-"APRStandard"
f16$attbox[f16$f3=="Ann"]<-"AnnualFee"
f16$attbox[f16$f3=="iAP"]<-"IntroRate"
f16$attbox[f16$f3=="iPe"]<-"AIntroPeriod"

f16$attbox<-as.factor(f16$attbox)

##simpler model with just the interaction by datasource
m4 <- glmer(fixations ~ newbeta.c*datasource + delta.c+(1|RecordingName), data = f16, family = poisson, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(m4)

##Full model with all interactions
m5 <- lmer(logfixations ~ newbeta.c*datasource*attbox+delta.c*datasource*attbox+(1|RecordingName), data = f16, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
summary(m5)

```

### 5.2. Plotting the relationship between beta and search for each attribute 


```{r}
plot(Effect(c("newbeta.c", "attbox"), m5))
```

